---
title: Material & Methods
date: "`r Sys.Date()`"
bibliography: references.bib
---

```{r}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)

library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(sf)
library(vegan)
library(kableExtra)
source("../R/misc.R") # Define your custom code as a bunch of functions.
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

#theme_set(theme_cowplot())

```
```{r}
myload(mynmds, envir = environment(), dir = get_mypath("data"))

```


## Data selection

We kept only the sites that did not suffer from amplication problem.
We concatenate replicates samples from sites that suffered from amplification
problems.

## Environmental variables

The coordinates of the sites, latitude and longitude, were recorded during
sampling events. The site distance from its string and the site altitude were
extracted thank to a stream network reconstruction. The stream network
reconstruction was done with the R packages `openStars` and `SSN`
[@kattwinkel_preparing_2020; @hoef_ssn:_2014].

## Statistical analysis


Community composition was analyzed through Non Metric Dimensional Scaling
(NMDS). The distance between community composition was computed with Bray-Curtis
distance. The representation of the community composition in the two dimensional
space was acceptable, with a stress value of `r round(mynmds$stress,2)`. To
explore how much the community composition, we fitted environmental variables
onto the ordination (`envfit` function in the `vegan` package). The
significativity of the fitted environmental variables through 999 permutations
of the community coordinates.

The species richness was modeled according to latitude, longitude, altitude and
distance from string and the interaction between latitude and longitude, with a
Poisson linear model. We found significative spatial autocorrelation in species
richness (Moran test: $I = 0.19$, $P = 0.005$, Figure SXX). Then we modeled
spatial correlation with an exponential correlation structure with `glmmPQL`
function in the `MASS` package. The validity of the model was assessed with the
visual inspection of the residuals.

To assess assembly rules of mussels communities, we computed the cooccurence between
species. Cooccurence patterns between species reflect the influence of
environmental constraints, species interactions and dispersal limitation. The
expected cooccurence between species pairs was compared to observed cooccurence.
The expected cooccurence between a species pair is simply the product of the
probability of occurrence of the two species multiplied by the total number of
sites [@griffith_cooccur_2016]. The significativity of the association was
assessed as ... with a threshold of 0.1, after the power analysis of
@veech_probabilistic_2013. Only the species pairs with an expected cooccurence
superior to 1 were kept in the analysis. Cooccurence analysis were done with the `cooccur` R package [@griffith_cooccur_2016].

All the analysis were performed in R v3.6.3 [@r_core_team_r_2020] and the
scripts used for the analysis are available online [https://github.com/alaindanet/prie_mussels](https://github.com/alaindanet/prie_mussels).

# References
